Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\mathbf{\sqrt{s_\mathrm{NN}} = 2.76}$~TeV

### 2016-11-07 paper.tex
Ante comments on model description and also latest figures

Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties.
In this article, we have extended that analysis to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also include extensive comparisons to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we present the details of the analysis methods. The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. Various theoretical models used in the article are described in Sec.~\ref{sec:models}. The results of the measurements are presented in Sec.~\ref{sec:results}.
 In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Sec.~\ref{sec:summary} summarizes our findings.

@@

One of the other largest contributions to the systematic uncertainty originates from the non-uniform reconstruction efficiency. In order to estimate the effects on the measurements of these azimuthal correlators for various detector inefficiencies, we use the AMPT models (see the details in Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles. Then we enforce detector inefficiencies by imposing non-uniform azimuthal distribution from the data. For the observables, SC(5,2), SC(5,3) and SC(4,3), the uncertainties from the non-uniform distribution of azimuthal angles were about 9\%, 17\% and 11\%, respectively.
Generally, systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$, because smaller values of $v_n$ are more sensitive to azimuthal modulation and $v_n$ decreases with $n$ increasing. 
%Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.
\section{Theoretical models}
\label{sec:models}
We have used various models in this article. The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency. 
%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}.

@@

The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} is an event-by-event theoretical framework model for relativistic heavy-ion collision based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP fluid and the highly dissipative and even off-equilibrium late hadronic stage with fluid-dynamics. With well tuned transport coefficients, decoupling temperature  and some well-chosen initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ parametrizations are used in the model~\cite{Zhu:2016puf}. 
Traditionally, the Glauber model constructs the initial entropy density of the QGP fireball from a mixture of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}. In the Monte-Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuations of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position space. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing parameter in the {AMPT} initial conditions makes the typical initial fluctuation scales changeable which gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions. The model then introduces the string melting procedure to produce initial partons. These partons are then evolved for the short duration using the ZPC parton cascade model. Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution. Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.

Finally, we provide an independent estimate of the centrality dependence of our observables by utilizing the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and energy. To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
The AMPT model can be run in two main configurations, the default and the string melting model.
In the default version, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}. In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final-state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on a Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
The third version presented in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$. 
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $\pt$ spectra, and $v_2$ of low-$\pt$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2760$~GeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the measurements. It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement. The detail configurations on AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.

@@

However, unlike SC$(m,n)$, NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)). NSC(4,3)) is comparable to NSC(3,2) and one finds that a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for most of centrality ranges within the errors.
These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also the individual flow strength. 
SC(5,2) is stronger than SC(5,3), but as for NSC, the correlation between $v_5$ and $v_3$ is stronger than the correlation between $v_5$ and $v_2$.

@@

The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
All the models with the large share viscosity regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than lower order harmonic correlations (SC(3,2), SC(4,2)).
And among the models with small shear viscosity ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the other initial conditions. 
A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to the data in 0-10\% central collisions. NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations while NSC(3,2) didn't show sensitivity to initial conditions or $\eta/s$ parametrizations.
SC(4,3) data is clearly favoured by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.

@@

>>>>

Recently, ALICE Collaboration measured for the first time the new multiparticle observables, the Symmetric 2-harmonic 4-particle Cumulants (SC), which quantify the relationship between event-by-event fluctuations of two different flow harmonics~\cite{ALICE:2016kpq}. 
The new observables are particularly robust against few-particle non-flow correlations and they provide orthogonal information to recently analysed symmetry plane correlators. 
It was demonstrated that they are sensitive to the temperature dependence of $\eta/s$ of the expanding medium and therefore simultaneous descriptions of different order harmonic correlations would constrain both the initial conditions and the medium properties.
In this article, we have extended that analysis to higher order Fourier harmonic (up to $5^{\mathrm{th}}$ order) correlations as well as to $p_{\rm T}$ dependence of correlations for the lower order harmonics ($v_3$-$v_2$ and $v_4$-$v_2$).  We also include extensive comparisons to hydrodynamic and AMPT model calculations.
In Sec.~\ref{sec:method} we summarize our findings from the previous work~\cite{ALICE:2016kpq} and present the analysis methods. The experimental setting and measurements are described in Sec.~\ref{sec:experiment} and the sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}. Various theoretical models used in the article are described in Sec.~\ref{sec:models}. The results of the measurements are presented in Sec.~\ref{sec:results}.
 In Sec.~\ref{sec:theory} we present comparisons to theoretical calculations. Sec.~\ref{sec:summary} summarizes our findings.

@@

One of the other largest contributions to the systematic uncertainty originates from the non-uniform reconstruction efficiency. In order to estimate the effects on the measurements of these azimuthal correlators for various detector inefficiencies, we use the AMPT models (see the details in Sec.~\ref{sec:theory}) which have flat uniform distribution of azimuthal angles. Then we enforce detector inefficiencies by imposing non-uniform azimuthal distribution from the data. For the observables, SC(5,2), SC(5,3) and SC(4,3), the uncertainties from the non-uniform distribution of azimuthal angles were about 9\%, 17\% and 11\%, respectively.
Generally, systematic uncertainties are larger for the SC(5,3) and SC(5,2) than for the lower harmonics of SC$(m,n)$, because smaller values of $v_n$ are more sensitive to azimuthal modulation and $v_n$ decreases with $n$ increasing. 
%Furthermore, the various AMPT models (see the details in Sec.~\ref{sec:theory}) were used to check the sensitivities of the observables due to the strength of the signals we are measuring, it turned out that the effect is negligible.

\section{Theoretical models}
\label{sec:models}
We have used various models in this article. The {HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum. 
%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}.

@@

The VISH2+1~\cite{Shen:2010uy,Shen:2014vra} is an event-by-event theoretical model for relativistic heavy-ion collisions based on (2+1)-dimensional viscous hydrodynamics which describes both the QGP phase and the highly dissipative and even off-equilibrium late hadronic stage with fluid dynamics. With well tuned transport coefficients, decoupling temperature  and some initial conditions (like {AMPT}~\cite{Xu:2016hmp,Bhalerao:2015iya,Pang:2012he} etc.), it could fit many related soft hadron data, such as the $p_{\rm T}$ spectra and different flow harmonics at RHIC and the LHC~\cite{Qiu:2011hf, Shen:2010uy, Shen:2011eg, Bhalerao:2015iya}.
Three different initial conditions ({MC-Glauber}, {MC-KLN} and {AMPT}) along with different constant $\eta/s$ values are used in the model~\cite{Zhu:2016puf}. 
Traditionally, the Glauber model constructs the initial entropy density of the QGP fireball from a mixture of the wounded nucleon and binary collision density profiles~\cite{Kolb:2000sd}, and the {KLN} model assumes that the initial entropy density is proportional to the initial gluon density calculated from the corresponding $k_T$ factorization formula~\cite{Kharzeev:2000ph}. In the Monte Carlo versions ({MC-Glauber} and {MC-KLN})~\cite{Miller:2007ri,Drescher:2006ca,Hirano:2009ah}, additional initial state fluctuations are introduced through the position fluctuations of individual nucleons inside the colliding nuclei. For the {AMPT} initial conditions~\cite{Bhalerao:2015iya,Pang:2012he,Xu:2016hmp}, the fluctuating energy density profiles are constructed from the energy decompositions of individual partons, which fluctuate in both momentum and position coordinate. Compared with the {MC-Glauber} and {MC-KLN} initial conditions, the additional Gaussian smearing parameter in the {AMPT} initial conditions makes the typical initial fluctuation scales changeable which gives rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.
%The AMPT initial conditions is basically HIJING with the location of the strings specified according to the sites of the nucleon nucleon collisions. The model then introduces the string melting procedure to produce initial partons. These partons are then evolved for the short duration using the ZPC parton cascade model. Instead the initial energy momentum tensor is directly fed into the hydrodynamic calculations, the energy density and the flow velocity are first obtained using the Landau condition and only the ideal fluid parts are used as the initial condition for the hydrodynamic evolution. Mini-jets from semi-hard parton scatterings are assumed to be locally thermalized through a Gaussian smearing and give rise to non-vanishing initial local flow velocities~\cite{Pang:2012he}.

Finally, we provide an independent estimate of the centrality dependence of our observables by utilizing the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved in collisions of very large nuclei and/or at extremely high energy, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium as a result of its finite volume and energy. To address such non-equilibrium many-body dynamics, AMPT has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
For the initial conditions, the AMPT model uses the spatial and momentum distributions of hard minijet partons and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
The AMPT model can be run in two main configurations, the default and the string melting model.
In the default version, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}. In the string melting version, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which also includes resonance decays.
The third version presented in this article is based on the string melting configuration, in which the hadronic rescattering phase is switched off to study its influence to the development of anisotropic flow.
The input parameters used in both configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$. 
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces particle yields, $\pt$ spectra, and $v_2$ of low-$\pt$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2760$~GeV~\cite{Lin:2014tya}, it was seen clearly in the recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the harmonic flow coefficients of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2760$~GeV. It turns out that the radial flow in AMPT is 25\% lower than the measured value at the LHC, which indicates that the unrealistically low radial flow in AMPT is responsible for the quantitative disagreement~\cite{Adam:2016nfo}. The details of configurations of AMPT settings used for this article and the comparisons of $p_{\rm T}$ differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.

@@

However, unlike SC$(m,n)$, NSC$(m,n)$ results with the higher order flow harmonics show almost same order of the correlation strength as the lower order flow harmonic correlations (NSC(3,2) or NSC(4,2)). NSC(4,3)) is comparable to NSC(3,2) and one finds that a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for centrality ranges $>20\%$ within the errors.  
These results indicate that the lower order harmonic correlations (SC(3,2) and SC(4,2)) are larger than higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)), not only because of the correlation strength itself but also the individual flow strength. 
SC(5,2) is stronger than SC(5,3), but as for NSC, the correlation between $v_5$ and $v_3$ is stronger than the correlation between $v_5$ and $v_2$.

@@

The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to VISH2+1 calculations~\cite{Zhu:2016puf}, shown in Fig.~\ref{fig:Figure_6}. 
All the models with the large share viscosity regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions, and $\eta/s=0.16$ for AMPT) failed to capture the centrality dependence of SC(5,2), SC(5,2) and SC(5,3), more clearly than lower order harmonic correlations (SC(3,2), SC(4,2)).
And among the models with small shear viscosity ($\eta/s=0.08$), the one from the AMPT initial condition describes the data much better than the other initial conditions. 
A quite clear separation between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
NSC(5,2) and SC(5,3) are quite sensitive to both the initial conditions and the $\eta/s$ parametrizations.
As similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the NSC(4,3) in these models is opposite to the data in 0-10\% central collisions. NSC(4,3) shows sensitivity to both initial conditions and $\eta/s$ parametrizations while NSC(3,2) didn't show sensitivity to initial conditions or $\eta/s$ parametrizations.
SC(4,3) data is clearly favored by smaller $\eta/s$ but NSC(4,3) cannot be described by these models quantitively.

@@

As discussed in Sec.~\ref{sec:results}, a hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3).
Except for 0-10\% centrality range, we found that the hierarchy NSC(5,3)$>$NSC(4,2)$>$NSC(5,2) also holds for Hydrodynamic calculations and AMPT models.
The observed difference between SC(5,2) and SC(5,3) (SC(5,2)$>$SC(5,3)) can be explained by the difference of the individual flow harmonics ($v_2$$>$$v_3$). 
The opposite trend are observed for the normalized SC (NSC(5,3)$>$NSC(5,2)). This can be attributed to the fact that the flow fluctuation is stronger for $v_3$ than $v_2$~\cite{Aad:2013xma}. It was claimed in Ref.~\cite{Zhu:2016puf} and seen also in Ref.~\cite{Bhalerao:2014xra} based on a AMPT model. 
NSC($m$,$n$) correlators increase with the larger $\eta/s$ in Hydrodynamic calculations in 0-30\% centrality range in the same way as the event-plane correlations~\cite{Bhalerao:2013ina,Teaney:2013dta}. In semi-peripheral collisions ($>$40\%), the opposite trend is observed.
